Gravitational-wave sensitivity curves

### 2014-07-02 noise_curve.tex
tweaks
new acknowledgements

\title{Gravitational-wave sensitivity curves}
\author{C J Moore$^1$, C P L Berry$^{1,\,2}$ \& R H Cole$^1$}
\address{$^1$ Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom}
\address{$^2$ School of Physics and Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom}
\ead{cjm96@ast.cam.ac.uk}

@@

\ack{Christopher Moore is supported by the STFC. I would like to thank Dr Jonathan Gair, Christopher Berry and Robert Cole for help producing this work. I would also like to thank Robert Cole for help producing the figures on the website. }

>>>>

\title{Gravitational-wave sensitivity curves}
\author{C J Moore$^1$, R H Cole$^1$ \& C P L Berry$^{1,\,2}$}
\address{$^1$ Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom}
\address{$^2$ School of Physics and Astronomy, University of Birmingham, Edgbaston, Birmingham B15 2TT, United Kingdom}
\ead{cjm96@ast.cam.ac.uk}

@@

\ack{C Moore and R Cole are supported by the STFC. C Berry is supported by ... We are indebted to Dr Jonathan Gair, for his useful advice and for proof-reading the manuscript.}
